Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-05-20 Paper Sigatoka - 2015.tex
20 mayo

In this work, we compare five machine learning techniques 
to predict the development rate of the black Sigatoka disease:
support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression.

The main contribution of this work is a comparison between machine
learning methods to forecast black Sigatoka development rate. 
\marginnote{FALTA COMPLETAR esta parte}

@@

\TODO{Revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
  \citep{XXX} por las referencias correspondientes (Pablo, 1/5/16)}

The early warning system developed by Ganry and Meyer \citep{XXX} for
the control of the yellow Sigatoka in Cameroon was adapted by Ganry
and Meyer \citep{XXX} for the black Sigatoka. 
%
%The early warning system for black Sigatoka \citep{XXX} is an
%adaptation of the yellow Sigatoka warning system developed by Ganry
%and Meyer \citep{XXX}.  It was modified by Ganry and Laville
%\citep{XXX} for its ito use for controlling yellow Sigatoka in
%Cameroon.
Ternesien and Fouré \citep{XXX} later improved Ganry and Laville's system.

The latter system is based on weekly quantified observations of
the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages.
%
The numeric coefficients describe the degree of incidence and the
severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.
\TODO{coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

@@

>>>>

In this work, we compare five machine learning techniques 
to predict the development rate of the black Sigatoka disease:
support
vector regression (SVR), echo state networks (ESN), ridge regression,
elastic-net regression and ordinary least squares linear regression.
%
The main contribution of this work is a comparison between machine
learning methods to forecast black Sigatoka development rate. 
\marginnote{FALTA COMPLETAR esta parte}

The outline of the paper is as follows. In Section 2, we present materials and methods of our research. In Section 3, we present the main results and their discussion. Our conclusions and future work are presented in Section 4.

@@

\TODO{ LISTO  Revisar si la nueva redacción de este párrafo coincide con la
  original.  Eso es lo que creo se quería decir, porque no quedaba
  claro cuál sistema fue creado por quién...  Las referencias a cada
  sistema en algo así son absolutamente necesarias.  Favor reemplazar
  {XXX} por las referencias correspondientes (Pablo, 1/5/16)}

The early warning system developed by Ganry and Meyer \citep{ganry1972} and modified by Ganry and Laville \citep{ganry1983} to use for controlling yellow Sigatoka in Cameroon, later was adapted for Ternesien \citep{Ternesien1985} and Fouré \citep{foure1988} for the black Sigatoka.

The latter system is based on weekly quantified observations of
the disease progression on young leaves of the plant, according to
Fouré's scale of the symptom stages.
%
The numeric coefficients describe the degree of incidence and the
severity of the disease development.  These coefficients are used to
calculate two variables: gross sum and state of evolution.

\TODO{ EN REALIDAD ASÍ ES USADO EN EL TEXTO FUENTE
coefficients??  No suena como coeficientes (un factor que
  multiplica términos en una función) sino como una calificación o
  nota o algo así (quizá ``grade''?).  ``Arbitrary coefficient'' no
  tiene sentido por el ``arbitrary''... No creo que sean tan
  arbitrarios sino predefinidos.  De hecho, el párrafo que sigue dice
  que suben con el avance de síntomas, es decir, no es tan
  ``arbitrario''.  Quizá querés decir ``arbitrarily chosen''?.  No
  estoy seguro si entiendo lo que se quiere decir aquí.}

@@

\section{Future work}
